Guide to repository of supplementary resources

### 2022-06-09 docs/index.Rmd
update index

---
title: "Guide to repository of supplementary resources"
date: ""`r format(Sys.time(), '%d %B, %Y')`""
output: html_document
---

@@

[Some animations of results (HTML page)](../experiments/3_animate/report.html)

>>>>

---
title: "Guide to repository of supplementary resources"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

[Some animations of results (HTML page)](./experiments/3_animate/report.html)
